\documentclass[PPFS.tex]{template/subfiles}
\begin{document}
%-----------------------------------
%	INTRODUCTION
%-----------------------------------
\section{Introduction}

The goal of this project is to create a system that will allow people, both clients and administrators, to interact with gyms in a modern and smart way. This system allows users to view what machines are currently open, and it also allows users to reserve systems for personal use. The system also provides gym administrators with the ability to understand more clearly what machines get used, along with how often and when they are used.

In order to accomplish this, sensors are placed on the gym equipment to detect whether or not it is in use. Displays are also placed on the equipment to show current or future reservations. These devices connect through a mesh network which communicates the information to a hub that then sends the data to server. A mesh network is a network where each device connects to those closest to it, and each device passes on information from one device to the next until the information makes it to the final location. It is through the server that reservations can be made on a hosted website and data for the gym can be utilized.

This project was done as the Senior Design Project for the Calvin College Engineering Department by team 14, which consists of Daniel DeHoog, Paul Griffioen, TJ DeVries, and Ryan Siekman. Senior Design is the capstone course for the Engineering degree at Calvin College and consists of a project chosen by the team, through which students learn about the development of task specifications, design process, team building, and design norms, where all of these are learned within a reformed Christian worldview. All the members of team 14 are Electrical/Computer Engineering Majors with Computer Science minors that will graduate in spring 2016.

\end{document}