\documentclass[ppfs.tex]{template/subfiles}
\begin{document}
%------------------------------------------
%	SYSTEM ARCHITECTURE
%------------------------------------------
\begin{comment}
    ----- Problem Statement -----
    It is helpful to provide a very simple block diagram of your project very early in the report to provide a
    graphical view that helps the reader understand. This diagram should focus on the interface(s) to your
    project. You may even show your project as a single block. This diagram can be more stylized (perhaps
    with clip art) to get the main idea across to the reader. 
    
    When you get to sections that explain your design process, start with the design of the system
    architecture. This is where you provide a detailed block diagram of your system. Be sure to justify your
    approach. Why did you break down the functionality of the system into the blocks as you did? Were
    there alternative ways to do it?

    In many cases, you may also include a block diagram of the hardware and a separate block diagram of the
    software (and perhaps a system block diagram to show how the two relate). Many teams make the
    mistake of describing the software with very little detail. It is highly recommended that you include a 
    block diagram of your software, preferably using the Uniform Modeling Language (UML).
\end{comment}

\section{System Architecture}

% Some introduction should go here that explains the general context

\subsection{Hub}

\subsection{Server}

\subsection{Sensors}

\subsection{Displays}

\end{document}
